---
title: "Food Sustainability Survey Insights"
author: "Elham Ali"
date: "2023-07-27"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)


# Install necessary packages
install.packages("dplyr")

# Load necessary libraries
library(dplyr)
library(readxl)
```

## Introduction

This report explores key data insights from a food sustainability survey administered to 1561 respondents who are either Registered Dietitian Nutritionist (RDN) or a Dietetic Technician, Registered (DTR) about current strategies, barriers, and competence in integrating food sustainability practices in their practices. 

The survey is administered by [Food + Planet](https://foodandplanet.org/) to understand the gaps in embedding sustainability in dietitian curricula. 

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

## Methods


# Results
## Graph 1: Average number of dietitians with sustainability education at the graduate levels

```{r setup, include=FALSE}

# Read the datasets
dataset1 <- read_excel("dataset 1.xlsx")
dataset2 <- read_excel("dataset 2.xlsx")
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
